---
title: "R Notebook"
output: html_notebook
---

```{r}
game_of_thrones

```

The frst thing I notice about this dataset is that is, again, stored in a different format to the other 2 datasets. I belive this to be stored as a list or nested list. I cna check this by running the folowing command:
```{r}
class(game_of_thrones)
```

it is indeed stored as a list.
further investigationof the dataset can be achieved by:

```{r}
str(game_of_thrones)
```
this shows that he data is based on the book rather than the TV series.

how many characters are male V female?
```{r}
male_characters <- sum(game_of_thrones[game_of_thrones$characters$gender == "Male"])
```
```{r}
male_characters <- sum(count(game_of_thrones[game_of_thrones$characters$gender == "Male"]))
```
```{r}
male_characters <- count[game_of_thrones$characters$gender == "Male"]
```
```{r}
length(game_of_thrones[game_of_thrones$characters[[1]]$gender == "Male"])
```
```{r}
as.matrix(game_of_thrones)
```

```{r}
genderList<- map(game_of_thrones$characters,"gender")
male_count <- length(genderList[1] == "Male")
male_count

```

```{r}
genderList
```

