---
title: "R Notebook"
output: html_notebook
---

Question 1
Load in the sunspots data and check it is a time series. Get the start, end, periodicity, frequency and cycle information. Get the start and end times, periodicity, frequency, and anything else you need to understand your data.

```{r}
data(sunspots)

head(sunspots)
class(sunspots)
str(sunspots)

start(sunspots)
end(sunspots)
#periodicity(sunspots)
frequency(sunspots)
cycle(sunspots)
plot.ts(sunspots)
```



Question 4
Decompose the time series and look at the different components. Make sure you use the right type of decomposition. Then take a look at your different components. What does it all tell you? Hint: you might need to subset some of your data in order to see patterns more clearly

```{r}
sun_decomp <- decompose(sunspots, type = "additive")
plot(sun_decomp)
```


Question 3
Calculate the rolling average of your sunspots data, and plot it. Hint: You’ll need to choose the window you want to average over to make sure it’s representative of this particular time series

```{r}
library(tidyquant)
library(zoo)
library(TTR)
rolling_average <- rollapply(sunspots, width = 60, align = "right", FUN = mean, na.rm = TRUE)
plot(rolling_average)

#rolling_log <- log(rolling_average)
#plot(rolling_log)
```

Question 5
Check if your data is stationary using the appropriate plots. Do you have stationary data? If no, make the data stationary.
```{r}
#log

#difference

#plot
```

