---
title: "R Notebook"
output: html_notebook
---

```{r}
data(anscombe)
?anscombe
str(anscombe)

```

1. x1, x2, x3, x4, y1, y2, y3, y4
2. find mean and variance 
```{r}
mean(anscombe$x1)
mean(anscombe$x2)
mean(anscombe$x3)
mean(anscombe$x4)
mean(anscombe$y1)
mean(anscombe$y2)
mean(anscombe$y3)
mean(anscombe$y4)
```
```{r}
?var
```

```{r}
var(anscombe$x1)
var(anscombe$x2)
var(anscombe$x3)
var(anscombe$x4)
var(anscombe$y2)
var(anscombe$y3)
var(anscombe$y4)
```

3. all x datsetes seem quite similar as do the y's. dont using only mena and variance can be misleading though. it is important to visualise the data for this reason.

4. Create box plots for the eight data sets and interpret what you see. Perhaps calculate IQR() and skewness() for each set. Should you change your conclusions from above?
```{r}
boxplot(anscombe$x1)
```

```{r}
boxplot(anscombe$x2)
```

```{r}
boxplot(anscombe$x3)
```

```{r}
boxplot(anscombe$x4)
```

```{r}
boxplot(anscombe$ y1)
```

```{r}
boxplot(anscombe$y2)
```

```{r}
boxplot(anscombe$y3)
```

```{r}
boxplot(anscombe$y4)
```

```{r}
boxplot(anscombe)
```

first three values all seem to be very similiar.
the 4th x value apears to be made up of a single vlalue range.
y1 seems to unimodal, with most of the values concentrtated in a small range within the cente.
y2 is right skwewed with one outlier.
y3 qnd y4 are quite similar althought he median differs in each.

```{r}
skewness(anscombe$x1)
skewness(anscombe$x2)
skewness(anscombe$x3)
skewness(anscombe$x4)
skewness(anscombe$y1)
skewness(anscombe$y2)
skewness(anscombe$y3)
skewness(anscombe$y4)

```

```{r}
IQR(anscombe$x1)
IQR(anscombe$x2)
IQR(anscombe$x3)
IQR(anscombe$x4)
IQR(anscombe$y1)
IQR(anscombe$y2)
IQR(anscombe$y3)
IQR(anscombe$y4)
```


```{r}

```

5. Anscombe intended his eight sets to be interpreted as four sets of (x,y) data: (x1,y1), (x2,y2), (x3,y3) and (x4,y4). Plot y1-vs-x1, y2-vs-x2, y3-vs-x3 and y4-vs-x4 using the plot() function and comment on what you observe.

```{r}
plot(anscombe$x1, anscombe$y1)
```


